\begin{moduledoc}{Learning stopped by periods or learning error}{learnSNNS}
  \item[\KeyWord{learnfct} \optParam{ x } ]~\\
    This parameter $x$  contains the name of the SNNS-learning function.\\
    Default: Rprop
  \item[\KeyWord{learnparam} \optParam{ x } ]~\\
    This array of parameters indicates the parameter for the SNNS learning function.
    The meaning of the parameters can differ from learning function to learning function.
    For details please see the SNNS manual.\\
    Default: 0.0 0.0 0.0 5.0 0.0
  \item[\KeyWord{maxepochs} \optParam{ x } ]~\\
    This parameter $x$ contains the maximum number of periods for the learning 
    algorithm. After this maximum the module {\it learnSNNS} will automatically stop the 
    learning function.\\
    Default: 50
  \item[\KeyWord{maxtss} \optParam{ x } ]~\\
    This parameter indicates the maximal tolerable learning error of the network.
    The error is normalized by the number of learning patterns and the number of output units.
    The module {\it learnSNNS} will terminate the learning function if the learning error
    is less then this threshold.\\
    Default: 0.5
  \item[\KeyWord{shuffle} \optParam{ x } ]~\\
    This switch indicates whether the sequence of the learning patterns is changed after
    each learning period or not.
    If the switch is turned on, then the module {\it learnSNNS} will use the
    SNNS-function {\it shuffle}\\
    Default: yes
\end{moduledoc}


The module {\it learnSNNS} is the standard-learn module during the optimization.
The module stops the learning of an offspring network if the learning error is below an 
upper bound or it reaches the maximum number of learning periods.


\algo{10cm}{learnSNNS}{
Set the SNNS learn function {\it learnFct};\\
{\bf for all} (networks of the offspring population) {\bf do}\\ 
\hspace*{0.5cm}{\bf while} (Epochs $<$ {\it maxEpochs}) {\bf and} 
               (tss $>$ {\it maxTss}) {\bf do}\\
\hspace*{1.0cm}Train one period with {\it learnParam};\\

}

