\begin{moduledoc}{Mutation of hidden neurons}{mutUnits}
  \item[\KeyWord{probMutUnits} \optParam{ x } ]~\\
    The parameter $x$ indicates the probability $p_{mut}$ a mutation takes 
    place.\\
    Default: 0.5
  \item[\KeyWord{probMutUnitsSplit} \optParam{ x } ]~\\
    The parameter $x$ describes the relationship between inserting and deleting
    hidden units.
    Default: 0.5
  \item[\KeyWord{PWU} \optParam{ x } ]~\\
    This switch activates the  {\it Prefer Weak Units} strategy in the case of deleting 
    hidden units.\\
    Default: yes
  \item[\KeyWord{bypass} \optParam{ x } ]~\\
    This switch turns on the {\it bypass} function while deleting a hidden unit.\\
    Default: yes
  \item[\KeyWord{initRange} \optParam{ x } ]~\\
    This parameter $x$ describes the interval [-initRange,initRange] where 
    inserted weights are randomly selected from.
    Default: 0.5
\end{moduledoc}

The module {\it mutUnits} executes a mutation of the hidden units.
The maximum number of deleted or inserted hidden units is limited by one.
All other mutation and optimization modules can only delete units, they can
never insert weights to a deleted hidden unit.
In this case of deleting an activated hidden unit, all weights will be deleted.
In the case of inserting a hidden unit, all possible weights will be inserted.
The number of weights and hidden units which can be inserted is limited by the 
topological structure of the reference net.
The modules uses {\it bypass}-function and the {\it Prefer Weak Unit} strategy.
The {\it bypass}-function is illustrated in figure \ref{bypass}. The idea is to
linearly approximate a non-linear relationship, i.e., approximate the function
computed by a hidden
unit by a linear function. This is done by using shortcut (direct) connections.
The  {\it Prefer Weak Unit} strategy is to check the connectivity of a unit, i.e.,
count its incoming and outgoing weights, and prefer those for deleting which are weaker
connected. This is called soft unit pruning. 

\algo{12cm}{mutUnits}{
{{\bf if} ( RAND(0,1) $> p_{mut}$ ) {\bf then}\\
\hspace*{0.5cm}{\bf if} ( RAND(0,1) $> p_{split}$ ) {\bf then}\\
\hspace*{1.0cm}search a unit in the reference net which does not exist in offspring;\\
\hspace*{1.0cm}insert this unit in the offspring;\\ 
\hspace*{1.0cm}insert all possible weights of the unit;\\
\hspace*{0.5cm}{\bf else}\\
\hspace*{1.0cm}{\bf if} ( PWU set ) {\bf then}\\
\hspace*{1.5cm}select the {\it weakest} hidden unit of the offspring;\\
\hspace*{1.0cm}{\bf else }\\
\hspace*{1.5cm}select accidental a hidden unit of the offspring;\\
\hspace*{1.0cm}{\bf if} ( bypass activated ) {\bf then}\\
\hspace*{1.5cm}delete the selected unit with the bypass function;\\
\hspace*{1.0cm}{\bf else}\\
\hspace*{1.5cm}delete the unit and all its weights;\\
}
}



